---
title: "Python code chunks in R Markdown"
date: "2018-02-22"
output: pdf_document
---

## A normal R code chunk

```{r}
library(reticulate)
x = 42
print(x)
```

## Modify an R variable

In the following chunk, the value of `x` on the right hand side
is `r x`, which was defined in the previous chunk.

```{r}
x = x + 12
print(x)
```

## A Python chunk

This works fine and as expected. 

```{python}
x = 42 * 2
print(x) 
```

The value of `x` in the Python session is `r py$x`.
It is not the same `x` as the one in R.

## Modify a Python variable

```{python}
x = x + 18 
print(x)
```

Retrieve the value of `x` from the Python session again:

```{r}
py$x
```

Assign to a variable in the Python session from R:

```{r}
py$y = 1:5
```

See the value of `y` in the Python session:

```{python}
print(y)
```


```{bash}
echo "Hello Bash!"
cd C:/Sashi/R_Projects/dsc520/data
cat Scores1.csv Scores1.csv > Scores12.csv
cat Scores12.csv
```

```{r}
library(DBI)
db = dbConnect(RSQLite::SQLite(), dbname = "sql.sqlite")
```

```{sql, connection=db, max.print = 20}
SELECT * FROM trials
```

